Identity signaling model progress

### 2020-02-13 reports/Progress-2-14-20.tex
disliking experiment ready for cluster

\author{{Matthew A.~Turner}}

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=0.8\textwidth]{Figures/exampleMidrangeSeries.pdf}
  \caption{Timeseries of nine combinations of $r/R$ and $w$.}
  \label{fig:exampleSeries}
\end{figure}

\begin{figure}[H]
  \centering
\includegraphics[width=0.8\textwidth]{Figures/covertDensityVsReceptivityHomophily.pdf}
  \caption{Density of covert signalers at $t=100$, final timestep recorded
    in this preliminary experiment.}
  \label{fig:}
\end{figure}

>>>>

\author{} %{Matthew A.~Turner}}

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=0.8\textwidth]{Figures/exampleMidrangeSeries.pdf}
  \caption{Timeseries of nine combinations of $r/R$ and $w$.}
  \label{fig:receptivityHomophilySeries}
\end{figure}

\begin{figure}[H]
  \centering
\includegraphics[width=0.8\textwidth]{Figures/covertDensityVsReceptivityHomophily.pdf}
  \caption{Density of covert signalers at $t=100$, final timestep recorded
    in this preliminary experiment.}
  \label{fig:receptivityHomophilyHeatmap}
\end{figure}

\subsection*{Density of covert signalers vs. disliking penalty $d=\delta$ and homophily, $w$}

Here we co-vary the disliking penalties, which we set equal ($d=\delta$), and
homophily, $w$. The bonus payoff for two interacting agents where at least one
likes the other is set to $s=0.25$. The payoff structure is as follows

\begin{table}[h]
  \centering
  \begin{tabular}{rl}
   Attitude combo. & Payoff \\
   \toprule
    Like/like & $1 + s$ \\
    Like/neutral & $1 + s$ \\
    Neutral/neutral & 1 \\
    Like/dislike & $1 + s - d$ \\
    Dislike/neutral & $1 - d$ \\
    Dislike/dislike & $1 - d - \delta$
  \end{tabular}
\end{table}

Specifically, we vary $d=\delta \in \{0.0, 0.05, 0.1, \ldots, 0.45\}
As in the above experiment, we set $w \in \{0.0, 0.5, \ldots, 0.45\}$.
In this experiment we ran the simulations to 200 timesteps 
(Figure~\ref{fig:dislikingHomophilySeries}).

\begin{figure}[H]
  \centering
  \includegraphics[width=0.8\textwidth]{Figures/exampleMidrangeSeries.pdf}
  \caption{Timeseries of nine combinations of $d=\delta$ and $w$.}
  \label{fig:dislikingHomophilySeries}
\end{figure}

\begin{figure}[H]
  \centering
\includegraphics[width=0.8\textwidth]{Figures/covertDensityVsReceptivityHomophily.pdf}
  \caption{Density of covert signalers at $t=100$, final timestep recorded
    in this preliminary experiment.}
  \label{fig:dislikingHomophilyHeatmap}
\end{figure}
